Structural Assessment on Stateless Blockchain Improvements with LRU-oriented Cache Replacement Policy

### 2020-06-22 abstract.tex
修正 6/22 會議後文法與用字問題

在本論文中，我們將在基於帳號的區塊鏈上討論以下兩點：
第一，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
只要快取帳號的訊息，
就可以省略部分交易的證明，
以此來減少網路流量與驗證時間。
第二，
快取替換有多種策略，針對 LRU 策略，
設計了基於不可變紅黑樹與不可變順序樹的兩種資料結構，
並且進行實驗比較了快取命中與快取失效的代價，
模擬現今以太坊的區塊性質，
當快取數十個區塊大小的賬戶資訊量時，
快取命中所需的查找時間仍數倍低於梅克爾 Patricia 證明驗證的時間。

@@

In this paper, we will discuss the following two points
on account-based blockchain.
First,
It is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

>>>>

在本論文中，我們將在基於賬號的區塊鏈上討論以下兩點：
第一，
一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
只要快取賬號的訊息，
就可以省略部分交易的證明，
以此來減少網路流量與驗證時間。
第二，
快取替換有多種策略，針對 LRU 策略，
設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
並且進行實驗比較了快取命中與快取失效的代價，
模擬現今以太坊的區塊性質，
當快取數十個區塊大小的賬戶資訊量時，
快取命中所需的查找時間仍數倍低於梅克爾 Patricia 證明驗證的時間。

@@

In this paper, we will discuss the following two points
on account-based blockchain.
First,
it is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
there are so many cache replacement polcies.
For LRU polices, we designed two composite data
structures which based on red-black tree and value-independent order tree.
And conduct some experiments to compare the cost of a
cache hit with the penalty of a cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.

### 2020-06-22 ctapc/paper.tex
修正 6/22 會議後文法與用字問題

In this paper, we will discuss the following two points
on account-based blockchain.
First,
It is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement polices.
For LRU polices, we designed two composite data
structures which based on red-black tree and order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
\end{abstract}

@@

\subsection{persistent LRU algorithm}
Before discussing persistent LRU algorithms, we first observe how to efficiently implement LRU cache on software. Judging from several popular LRU libraries on github, interior data structures are all combinations of hash table and doubly linked list.
While executing get, it will get the data by the pointer pointing to the node of list. Then, the node will move to the head of the list. While executing put, if cache hits, the value of node will be updated, and the node will move to the head of the list. If cache is not full, the cache value will be added to the head and the pointer will be put in the hash table. Instead, if the cache is full, pull out the tail node of the doubly linked list, and delete the old key in the hash table. Then, add cache value to the head and put the pointer in the hash table.
We observed that there are two kinds of information that need to be recorded by LRU.
\begin{enumerate}
  \item find the value from key (key-value pair)
  \item the order information of all keys
\end{enumerate}
In the implementation of combinations of hash table and doubly linked list, hash table is responsible for (1), and doubly linked list is responsible for (2). We observed that a doubly linked list records the order relationship naturally, and it doesn't even need to record the definite using time.
There is one simple idea that we directly combine persistent-versioned alternatives of a hash table and a doubly linked list, and then we get a persistent LRU. Although there are mature alternatives~\cite{b5}~\cite{b6} for hash tables, it is hard to find such a thing for doubly linked lists.
Thus, we need to use other persistent and efficient data structures to replace doubly linked lists. The things that an abstract doubly linked list can do are as follows.
\begin{itemize}
\item Update the using time of node to latest
\item Delete the least recently used node
\item Insert new node and update the using time of the node to latest
\end{itemize}
Following we will discuss how to use red-black tree~\cite{b7} to complete the above tasks and introduce our design of order tree, which is more efficient than red-black tree.

@@

\subsection{hash table + order tree}
Doubly linked list records order relations by the pointer relations of nodes. Red-black tree has to additionally record the timestamp. Moreover, the account’s information that we can search with the hash table in one time now needs two steps with red-black tree; namely, we find the timestamp from the address, and then find the account's information from the timestamp.
The reason why doubly linked lists cannot turn into persistent data structure through path copying is that two adjacent nodes always point to each other. Once modifying the node by path copying, it has to copy the whole list. Therefore, we want to find another way to connect the nodes.

Image to weave a net behind the nodes, and then stick them together.
The basic form of the net structure is a full binary tree. We name the structure using a full binary tree to store order data as order tree. We will introduce the operations of order tree as follows.

If cache size is n, the height of the order tree will be set as 1 + log n. That is to say, the number of leaves is at least two times the cache size. Fig. 3 shows that there is an order tree with size 4, and it has 8 leaf nodes.

Applying to LRU cache, the value stored by the hash table is a pointer pointing to the leaf node of the order tree. It only needs one time to get the data by searching the hash table. 
Order tree stores the entire data in leaf nodes, and each data is arranged in the order of time. In this paper, the newer the data, the more the right side of the leaf position. We will explain and draw in this way.

Some leaf nodes in the order tree have stored data, while some of them haven’t. We call the leaf with data as “used leaf”, and the leaf without data as “unused leaf”.
While executing get, change the used leaf into an unused leaf if it has been searched, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf. While executing put, first find the leftmost used leaf and change it into unused, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf. No matter get or put, it always occupies a leaf on the right. If the used leaf is on the rightmost of the tree, it has to execute full copy. Therefore, make all the used leaves tightly packed together to the left side of the new order tree in the original order.

Fig. 4 shows a series of execution of order tree. In this figure, full copy happens at the time when state 6 turns into state 7. The light blue nodes in the figure mean that they are unused. Notice that we painted all unused leaves of subtree light blue.
In implementation, there is no need to allocate memory space to light blue nodes. The pointer pointing to light blue subtree is a null pointer.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../images/order-tree}
  \caption{order tree with size 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../images/order-trees}
  \caption{order tree multiple operation}
\end{figure}

\subsubsection{complexity analysis}
In the following analysis, the size of the order tree is $n$.
If full copy doesn’t happen, execution of get and put go through root to leaf two times.
The height of the order tree is $O(\log n)$, and the time and space complexity are both $O(\log n)$.

If full copy happens, it has to go through the order tree,
and has all used leaves congregate to form a new tree.
Notice that the total number of nodes of a full binary tree is two times the quantity of leaves minus one,
and the total number won’t exceed $8*n$.
Therefore, the time and space complexity are both $O(n)$.

@@

\begin{itemize}
\item hash table + doubly-linked list, it will copy itself when creating a new version
\item persistent hash table + persistent red-black tree
\item persistent hash table + persistent order tree
\end{itemize}

@@

We claim that, in our implementation:
Hash table is unordered\_map in C++ standard library.
For persistent hash table, we use famous C++
persistent data structures library immer.
Doubly-linked list, persistent red-black tree,
persistent order tree are all implemented by ourselves.

From now on, we will refer to these three composite data structures
as doubly linked list, red-black tree, and order tree.

@@

The growth curve of the red-black tree and the sequence
tree is rather gentle ($O(\log n)$).
Noting that the line graph of the order tree,
compared to the smooth growth of the red-black tree,
is somewhat oscillating,
Because the number of leaves of the
order tree is $1 + \lceil \log_2 n \rceil$,
its number of leaves is more discrete,
When the cache size reaches the power of $2^k$,
the number of leaves doubles, which will affect
the performance and cause oscillating.

@@

From Fig 7 we can know that, when cache size is 30000,
put rate is 100\%, hit rate is 1.0, order tree implementation
can process 1000 blocks in 1.241 seconds, that means 
the average time to process a block is 1.241 milliseconds.
This number will be smaller when the cache size is smaller.

We chose Merkle Patricia tree verification cost to compare
with the order tree implementation,
We choose trie-db module,
which is a part of one of the two major
Ethereum implementations,
Parity Ethereum, to conduct experiment.

@@

The Experiments verify that order tree and red-black tree
have lower time complexity. When the cache size increases
to a certain extent, they significantly beat ever-copy
doubly linked list in performance. Compared with
red-black tree, order tree does not need to maintain
the color of the node, and to execute various rotation rules,
There is a little advantage in execution speed.

@@

\section{Conclusion}
This paper describes the design of shallow state blockchain and discusses the advantages and disadvantages of multiple cache strategies.
Especially for the LRU cache strategy, 
we first try the combination of persistent hash table and persistent red-black trees,
Further proposed a novel data structure, order tree, let it be combined with persistent hash,
Get a more efficient implementation of persistent LRU.

>>>>

In this paper, we will discuss the following two points
on account-based blockchain.
First,
It is highly possible to infer the validity of
a transaction from another valid transaction appearing recently.
If we cache account information, we can eliminate some
proof in transactions and then reduce network traffic
and verification time.
Second,
There are so many cache replacement policies.
For LRU policies, we designed two composite data
structures which based on red-black tree and value-independent order tree.
And conduct some experiments to compare the costs of
cache hit with the penalty of cache miss.
Simulating today's Ethereum's block property,
when cache size can contain several tens of blocks' information,
the cache searching time is significantly lower than
the time to verify Merkle Patricia proofs.
\end{abstract}

@@

\subsection{persistent LRU algorithm}
Before discussing persistent LRU algorithms, we first observe how to efficiently implement LRU cache on software. Judging from several popular LRU libraries on github, interior data structures are all combinations of hash table and doubly linked list.
While executing get, it will get the data by the pointer pointing to the node of list. Then, the node will move to the head of the list. While executing put, if cache hits, the value of node will be updated, and the node will move to the head of the list. If cache is not full, the cache value will be added to the head and the pointer will be put in the hash table. Instead, if the cache is full, pull out the tail node of the doubly linked list, and delete the old key in the hash table. Then, add cache value to the head and put the pointer in the hash table.
We observed that there are two kinds of information that need to be recorded by LRU.
\begin{enumerate}
  \item find the value from key (key-value pair)
  \item the order information of all keys
\end{enumerate}
In the implementation of combinations of hash table and doubly linked list, hash table is responsible for (1), and doubly linked list is responsible for (2). We observed that a doubly linked list records the order relationship naturally, and it doesn't even need to record the definite using time.
There is one simple idea that we directly combine persistent-versioned alternatives of a hash table and a doubly linked list, and then we get a persistent LRU. Although there are mature alternatives~\cite{b5}~\cite{b6} for hash tables, it is hard to find such a thing for doubly linked lists.
Thus, we need to use other persistent and efficient data structures to replace doubly linked lists. The things that an abstract doubly linked list can do are as follows.
\begin{itemize}
\item Update the using time of node to latest
\item Delete the least recently used node
\item Insert new node and update the using time of the node to latest
\end{itemize}
Following we will discuss how to use red-black tree~\cite{b7} to complete the above tasks and introduce our design of value-independent order tree, which is more efficient than red-black tree.

@@

\subsection{hash table + value-independent order tree}
Doubly linked list records order relations by the pointer relations of nodes. Red-black tree has to additionally record the timestamp. Moreover, the account’s information that we can search with the hash table in one time now needs two steps with red-black tree; namely, we find the timestamp from the address, and then find the account's information from the timestamp.
The reason why doubly linked lists cannot turn into persistent data structure through path copying is that two adjacent nodes always point to each other. Once modifying the node by path copying, it has to copy the whole list. Therefore, we want to find another way to connect the nodes.

Image to weave a net behind the nodes, and then stick them together.
The basic form of the net structure is a full binary tree. We name the structure using a full binary tree to store order data as value-independent order tree. We will introduce the operations of value-independent order tree as follows.

If cache size is n, the height of the value-independent order tree will be set as 1 + log n. That is to say, the number of leaves is at least two times the cache size. Fig. 3 shows that there is an value-independent order tree with size 4, and it has 8 leaf nodes.

Applying to LRU cache, the value stored by the hash table is a pointer pointing to the leaf node of the value-independent order tree. It only needs one time to get the data by searching the hash table. 
value-independent order tree stores the entire data in leaf nodes, and each data is arranged in the order of time. In this paper, the newer the data, the more the right side of the leaf position. We will explain and draw in this way.

Some leaf nodes in the value-independent order tree have stored data, while some of them haven’t. We call the leaf with data as “used leaf”, and the leaf without data as “unused leaf”.
While executing get, change the used leaf into an unused leaf if it has been searched, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf. While executing put, first find the leftmost used leaf and change it into unused, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf. No matter get or put, it always occupies a leaf on the right. If the used leaf is on the rightmost of the tree, it has to execute full copy. Therefore, make all the used leaves tightly packed together to the left side of the new value-independent order tree in the original order.

Fig. 4 shows a series of execution of value-independent order tree. In this figure, full copy happens at the time when state 6 turns into state 7. The light blue nodes in the figure mean that they are unused. Notice that we painted all unused leaves of subtree light blue.
In implementation, there is no need to allocate memory space to light blue nodes. The pointer pointing to light blue subtree is a null pointer.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../images/order-tree}
  \caption{value-independent order tree with size 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../images/order-trees}
  \caption{value-independent order tree multiple operation}
\end{figure}

\subsubsection{complexity analysis}
In the following analysis, the size of the value-independent order tree is $n$.
If full copy doesn’t happen, execution of get and put go through root to leaf two times.
The height of the value-independent order tree is $O(\log n)$, and the time and space complexity are both $O(\log n)$.

If full copy happens, it has to go through the value-independent order tree,
and has all used leaves congregate to form a new tree.
Notice that the total number of nodes of a full binary tree is two times the quantity of leaves minus one,
and the total number won’t exceed $8*n$.
Therefore, the time and space complexity are both $O(n)$.

@@

\begin{itemize}
\item hash table + doubly-linked list, it will copy itself when creating a new version
\item persistent hash table + persistent red-black tree
\item persistent hash table + persistent value-independent order tree
\end{itemize}

@@

We claim that, in our implementation:
Hash table is unordered\_map in C++ standard library.
For persistent hash table, we use famous C++
persistent data structures library immer.
Doubly-linked list, persistent red-black tree,
persistent value-independent order tree are all implemented by ourselves.

From now on, we will refer to these three composite data structures
as doubly linked list, red-black tree, and value-independent order tree.

@@

The growth curve of the red-black tree and the sequence
tree is rather gentle ($O(\log n)$).
Noting that the line graph of the value-independent order tree,
compared to the smooth growth of the red-black tree,
is somewhat oscillating,
Because the number of leaves of the
value-independent order tree is $1 + \lceil \log_2 n \rceil$,
its number of leaves is more discrete,
When the cache size reaches the power of $2^k$,
the number of leaves doubles, which will affect
the performance and cause oscillating.

@@

From Fig 7 we can know that, when cache size is 30000,
put rate is 100\%, hit rate is 1.0, value-independent order tree implementation
can process 1000 blocks in 1.241 seconds, that means 
the average time to process a block is 1.241 milliseconds.
This number will be smaller when the cache size is smaller.

We chose Merkle Patricia tree verification cost to compare
with the value-independent order tree implementation,
We choose trie-db module,
which is a part of one of the two major
Ethereum implementations,
Parity Ethereum, to conduct experiment.

@@

The Experiments verify that value-independent order tree and red-black tree
have lower time complexity. When the cache size increases
to a certain extent, they significantly beat ever-copy
doubly linked list in performance. Compared with
red-black tree, value-independent order tree does not need to maintain
the color of the node, and to execute various rotation rules,
There is a little advantage in execution speed.

@@

\section{Conclusion}
This paper describes the design of shallow state blockchain and discusses the advantages and disadvantages of multiple cache strategies.
Especially for the LRU cache strategy, 
we first try the combination of persistent hash table and persistent red-black trees,
Further proposed a novel data structure, value-independent order tree, let it be combined with persistent hash,
Get a more efficient implementation of persistent LRU.
